Effectiveness of visual test in linear regression diagnositics

### 2022-07-27 paper_comparison/paper_comparison/paper_comparison.Rmd
include more plots in experimental design

```{r different-shape-of-herimite}
VI_MODEL$plot(poly_model(shape = 1, x = rand_uniform(), e = 0.5)$gen(300)) + ggtitle(quote(He[2]:"U shape")) -> p1
VI_MODEL$plot(poly_model(shape = 2, x = rand_uniform(), e = 0.5)$gen(300)) + ggtitle(quote(He[3]:"S shape")) -> p2
VI_MODEL$plot(poly_model(shape = 3, x = rand_uniform(), e = 0.5)$gen(300)) + ggtitle(quote(He[6]:"M shape")) -> p3
VI_MODEL$plot(poly_model(shape = 4, x = rand_uniform(), e = 0.5)$gen(300)) + ggtitle(quote(He[18]:"Triple-U shape")) -> p4

@@

The range of $\sigma$ was chosen so that estimates of the power would produce reasonably continuous power curves, comparable to that calculated for the conventional test. The values for $\boldsymbol{X}_{raw}$ were generated randomly and independently from one of the following four distributions: (1) $U(a = -1, b = 1)$, (2) $N(\mu = 0, \sigma = 0.3)$, (3) $lognormal(\mu = 0, \sigma = 0.6)/3$ and (4) $u\{a = 1, b = 5\}$. The uniform and the normal distribution are symmetric and commonly assumed. The adjusted log-normal distribution provides skewered density. The discrete uniform distribution provides discreteness in residual plot, which could enrich the pool of visual patterns. Three replications are made for each of the parameter values shown in [table ref here] and thus, 192 different lineups. For each lineup, the null model was fit to the actual dataset to obtain residuals and parameter estimates. The actual data plot was drawn as standard residual plot with raw residuals on the y-axis and fitted values on the x-axis. The 19 null datasets were generated by the residual rotation technique, and plotted in the same way. The actual data plot was randomly placed among these null dadta plots to produce the lineup. [figure ref here] is an example of one of these lineups. It was generated for $n = 1$, $\sigma = 1$, $j = 1$, $X_{raw} \sim N$. For this lineup, x out of k observers picked the actual data plot. Each lineup is evaluated by 5 different subjects to provide reasonable estimates of the p-value.

>>>>

```{r different-shape-of-herimite}
stand_dist <- function(x) (x - min(x))/max(x - min(x)) * 2 - 1

ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300)

VI_MODEL$plot(ori_dat) + ggtitle(quote(He[2]:"U shape")) -> p1
VI_MODEL$plot(poly_model(shape = 2, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote(He[3]:"S shape")) -> p2
VI_MODEL$plot(poly_model(shape = 3, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote(He[6]:"M shape")) -> p3
VI_MODEL$plot(poly_model(shape = 4, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.05)$gen(300, computed = select(ori_dat, x, e))) +
  ggtitle(quote(He[18]:"Triple-U shape")) -> p4

@@

The range of $\sigma$, which is a factor controlling the strength of the signal, was chosen so that different difficulty levels of lineups were generated and the estimated power curve would be smooth and continuous. Four different distribution were used to genearte $\boldsymbol{X}_raw$.

```{r different-sigma}
ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300)

VI_MODEL$plot(ori_dat) + ggtitle(quote(sigma~"="~0.5)) -> p1
VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 1)$gen(300, computed = select(ori_dat, x))) +
  ggtitle(quote(sigma~"="~1)) -> p2
VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 2)$gen(300, computed = select(ori_dat, x))) +
  ggtitle(quote(sigma~"="~2)) -> p3
VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 4)$gen(300, computed = select(ori_dat, x))) +
  ggtitle(quote(sigma~"="~4)) -> p4

The uniform and the normal distribution are symmetric and commonly assumed in statistical model. The adjusted log-normal distribution provides skewed density. And the discrete uniform distribution provides discreteness in residual plot, which could enrich the pool of visual patterns.

```{r different-dist}
ori_dat <- poly_model(shape = 1, x = {raw_x <- rand_uniform(-1, 1); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300)

VI_MODEL$plot(ori_dat) + ggtitle(quote(U(-1,1))) -> p1
VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_normal(sigma = 0.3); closed_form(~stand_dist(raw_x))}, sigma = 0.5)$gen(300, computed = select(ori_dat, e))) +
  ggtitle(quote(N(0,0.3))) -> p2
VI_MODEL$plot(poly_model(shape = 1, x = {raw_x <- rand_lognormal(sigma = 0.6); closed_form(~stand_dist(raw_x/3 - 1))}, sigma = 0.5)$gen(300, computed = select(ori_dat, e))) +
  ggtitle(quote(lognormal(0,0.6)/3)) -> p3
VI_MODEL$plot(poly_model(shape = 1, x = rand_uniform_d(k = 5, even = TRUE), sigma = 0.5)$gen(300, computed = select(ori_dat, e))) +
  ggtitle(quote(U~"{1,5}")) -> p4

Three replications are made for each of the parameter values shown in [table ref here] and thus, 192 different lineups. For each lineup, the null model was fit to the actual dataset to obtain residuals and parameter estimates. The actual data plot was drawn as standard residual plot with raw residuals on the y-axis and fitted values on the x-axis. The 19 null datasets were generated by the residual rotation technique, and plotted in the same way. The actual data plot was randomly placed among these null dadta plots to produce the lineup. [figure ref here] is an example of one of these lineups. It was generated for $n = 1$, $\sigma = 1$, $j = 1$, $X_{raw} \sim N$. For this lineup, x out of k observers picked the actual data plot. Each lineup is evaluated by 5 different subjects to provide reasonable estimates of the p-value.

### 2022-07-27 paper_comparison/paper_comparison/paper_comparison.tex
include more plots in experimental design

The range of \(\sigma\) was chosen so that estimates of the power would
produce reasonably continuous power curves, comparable to that
calculated for the conventional test. The values for
\(\boldsymbol{X}_{raw}\) were generated randomly and independently from
one of the following four distributions: (1) \(U(a = -1, b = 1)\), (2)
\(N(\mu = 0, \sigma = 0.3)\), (3) \(lognormal(\mu = 0, \sigma = 0.6)/3\)
and (4) \(u\{a = 1, b = 5\}\). The uniform and the normal distribution
are symmetric and commonly assumed. The adjusted log-normal distribution
provides skewered density. The discrete uniform distribution provides
discreteness in residual plot, which could enrich the pool of visual
patterns. Three replications are made for each of the parameter values
shown in {[}table ref here{]} and thus, 192 different lineups. For each
lineup, the null model was fit to the actual dataset to obtain residuals
and parameter estimates. The actual data plot was drawn as standard
residual plot with raw residuals on the y-axis and fitted values on the
x-axis. The 19 null datasets were generated by the residual rotation
technique, and plotted in the same way. The actual data plot was
randomly placed among these null dadta plots to produce the lineup.
{[}figure ref here{]} is an example of one of these lineups. It was
generated for \(n = 1\), \(\sigma = 1\), \(j = 1\), \(X_{raw} \sim N\).
For this lineup, x out of k observers picked the actual data plot. Each
lineup is evaluated by 5 different subjects to provide reasonable
estimates of the p-value.

>>>>

The range of \(\sigma\), which is a factor controlling the strength of
the signal, was chosen so that different difficulty levels of lineups
were generated and the estimated power curve would be smooth and
continuous. Four different distribution were used to genearte
\(\boldsymbol{X}_raw\).

\includegraphics{paper_comparison_files/figure-latex/different-sigma-1.pdf}

The uniform and the normal distribution are symmetric and commonly
assumed in statistical model. The adjusted log-normal distribution
provides skewed density. And the discrete uniform distribution provides
discreteness in residual plot, which could enrich the pool of visual
patterns.

\includegraphics{paper_comparison_files/figure-latex/different-dist-1.pdf}

Three replications are made for each of the parameter values shown in
{[}table ref here{]} and thus, 192 different lineups. For each lineup,
the null model was fit to the actual dataset to obtain residuals and
parameter estimates. The actual data plot was drawn as standard residual
plot with raw residuals on the y-axis and fitted values on the x-axis.
The 19 null datasets were generated by the residual rotation technique,
and plotted in the same way. The actual data plot was randomly placed
among these null dadta plots to produce the lineup. {[}figure ref
here{]} is an example of one of these lineups. It was generated for
\(n = 1\), \(\sigma = 1\), \(j = 1\), \(X_{raw} \sim N\). For this
lineup, x out of k observers picked the actual data plot. Each lineup is
evaluated by 5 different subjects to provide reasonable estimates of the
p-value.
